Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)

### 2024-08-05 doc/manuscript/ForC-EFDB manuscript.Rmd
add Besnard data reference

nocite: |
  @harris_updated_2014; @jung_exploiting_2006; @besnard_mapping_2021
---

@@

![**Figure `r fig_histograms`. Histograms of number of independent records in ForC relevant (grey) and submitted (black) to EFDB (both left axis), along with the relative global area of each type (red, right axis), organized by (a) dominant vegetation type, (b) FAO ecozone, (c) continent, and (d) stand age.** For dominant vegetation (a), 'Other' includes deciduous needleleaf, mixed broadleaf- needleleaf, non-woody vegetation (e.g., early successional), and incompletely classified or mixed forest types. Global coverage of each was obtained from SYNMAP (Jung *et al*, 2006). For FAO ecozones (b), codes are as listed in the caption of Figure `r fig_map`. The relative area of forests by age class was obtained from the global forest age database of Besnard *et al.* (2021), updated in 2024 (DOI: xxx).  ](figures_tables/Histogram_n_Relevant_and_Transferred_Records.png)

>>>>

nocite: |
  @harris_updated_2014; @jung_exploiting_2006; @besnard_mapping_2021; @besnard_global_2024
---

@@

![**Figure `r fig_histograms`. Histograms of number of independent records in ForC relevant (grey) and submitted (black) to EFDB (both left axis), along with the relative global area of each type (red, right axis), organized by (a) dominant vegetation type, (b) FAO ecozone, (c) continent, and (d) stand age.** For dominant vegetation (a), 'Other' includes deciduous needleleaf, mixed broadleaf- needleleaf, non-woody vegetation (e.g., early successional), and incompletely classified or mixed forest types. Global coverage of each was obtained from SYNMAP (Jung *et al*, 2006). For FAO ecozones (b), codes are as listed in the caption of Figure `r fig_map`. The relative area of forests by age class was obtained from the global forest age database of Besnard *et al.* (2021, 2024).  ](figures_tables/Histogram_n_Relevant_and_Transferred_Records.png)
